\bf A Hierarchical Bayesian Approach for Modeling Infant-Mortality and Wearout Failure Modes

### 2017-08-09 paper/paper.tex
Fix plot for Example 1.  Started work on new Conclusion.

With field data on consumer products, model-based appproaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of these, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate.

@@

%\begin{figure}[H]
%\centering
%\includegraphics{np_ex1}
%\caption{Top: Lifetime plot of data from 75 randomly selected units of drive-model `14'. Bottom: Kaplan-Meier estimate for drive-model `14'.}
%\label{dm14}
%\end{figure}

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{drive14cred.pdf}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws.  Solid blue line is a non-parametric Kaplan-Meier estimator.  Credible 90\% bands are in red.  Greenwood non-parametric error bands are in blue.}
  \label{fig1}
\end{figure}

@@

\section{Conclusions}
\label{sec:Conclusions}
We should point out some assumptions made in this analysis. First, we assume exchangability of units within drive-models. This assumption is due to our ignorance about the causes of failure and of potentially important covariates. If we had information about distinguishing characteristics of the two identified failure modes, then we should use this information. Also, there could be many environmental or human-related factors that impact lifetime, such as operating conditions associated with location in the data center, which are likely confounded with drive-model.

>>>>

With field data on consumer products, model-based approaches to inference require a model with sufficient flexibility to account for multiple kinds of failure. The causes of these, while not interesting to the consumer per se, can lead to various observed lifetime distributions. Because of this, standard lifetime models, such as Weibull or lognormal may be inadequate.

@@

@@

\begin{figure}[H]
\centering
  \includegraphics[width=.8\textwidth]{mod14_example1.pdf}
  \caption{Estimated GLFP for drive-model 14 plotted on Weibull paper.  Dashed line corresponds to the median of the posterior draws.  Solid line is a non-parametric Kaplan-Meier estimator.  Credible 90\% bands are in red.  Greenwood non-parametric error bands are in gray.}
  \label{fig1}
\end{figure}

@@

\section{Discussion}
\label{sec:Discussion}
This paper has shown how to model and make inference for the kind of product reliability data commonly found in the field.  Products with long lifetimes often have few failures and when failures do occur the cause is frequently unknown to the analyst.  The hierarchical GLFP model provides a unified framework to accurately model data with multiple failure modes, and provide a measure of uncertainty.  Moreover, when there are multiple brands within the same product class, the hierarchical approach allows the model to borrow strength from brands with lots of failures in order to fit and make inference for groups with little information.  This is extremely advantageous since many products have time (e.g., left truncation and right censoring) and resource constraints (unidentified failure modes) that limit the amount of information in the data.  This makes standard parametric lifetime models inaccurate and difficult to estimate using classical estimation techniques such as ML.

We should point out some assumptions made in this analysis. First, we assume exchangability of units within drive-models. This assumption is due to our ignorance about the causes of failure and of potentially important covariates. If we had information about distinguishing characteristics of the two identified failure modes, then we should use this information. Also, there could be many environmental or human-related factors that impact lifetime, such as operating conditions associated with location in the data center, which are likely confounded with drive-model.
